Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 policies.tex
Remove sub-flow policy.

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[sub-flow dropping]{
    \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
    \label{fig:policies.min_drop}
  }
  \end{center}
  \vspace{-0.2in}
  \caption{Comparison of dropping policies. Blue (dark) nodes indicate where
  dropping decisions are made.}
  \label{fig:policies.policies}
\end{figure}

@@

% Slack tracking module
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/policy_trade_off.pdf}
    \vspace{-0.3in}
    \caption{Slack tracking and drop decision hardware.}
    \label{fig:policies.trade_off}
    \vspace{-0.2in}
  \end{center}
\end{figure}

Another possible method is to make the dropping decisions somewhere in between
source-only dropping and unrestricted dropping. From the graph in 
Figure~\ref{fig:policies.dataflow_graph}, we can see that if the dropping
decision is made at event {\tt C} then we can skip event {\tt E} with no wasted
work. If we instead choose to perform monitoring for event {\tt C}, then we want to perform all
monitoring on that flow. Similarly, event {\tt F} creates a decision point for
the bottom flow that will result in no wasted work and dropping event {\tt A}
allows the entire shown metadata flow to be dropped with no wasted work. If the
program can be
analyzed or profiled to identify these instructions which, if dropped, lead to
no wasted work, then this information can be used at run-time to minimize the
amount of wasted work. We refer to this policy as \emph{sub-flow dropping}.
Figure~\ref{fig:policies.min_drop} shows the points were dropping decisions are
made for this policy.
Sub-flow dropping is a coarser-grained decision than unrestricted dropping, but
finer-grained that source-only dropping. Thus, its ability to match overheads is
expected to sit between these other two policies. Similarly, there still exists
edge cases where wasted work can occur, but typically we expect much less
wasted work than unrestricted 
dropping. Thus, we expect the coverage achieved by sub-flow dropping for a
certain overhead to fall between source-only and unrestricted dropping. These three
dropping policies create a trade-off space between coverage achieved and
ability to match an overhead target.
Figure~\ref{fig:policies.trade_off} summarizes this trade-off between coverage
and ability to match overhead.

>>>>

\begin{figure}
  \begin{center}
  \subfloat[unrestricted dropping]{
    \includegraphics[width=\columnwidth]{figs/all_drop.pdf}
    \label{fig:policies.all_drop}
  }
  \vspace{-0.1in}
  \\
  \subfloat[source-only dropping]{
    \includegraphics[width=\columnwidth]{figs/source_drop.pdf}
    \label{fig:policies.source_drop}
  }
  \vspace{-0.1in}
%   \\
%   \subfloat[sub-flow dropping]{
%     \includegraphics[width=\columnwidth]{figs/min_drop.pdf}
%     \label{fig:policies.min_drop}
%   }
  \end{center}
  \vspace{-0.1in}
  \caption{Comparison of dropping policies. Blue (dark) nodes indicate where
  dropping decisions are made.}
  \label{fig:policies.policies}
\end{figure}

@@

% Trade-off between source-drop and unrestricted dropping
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/policy_trade_off.pdf}
%     \vspace{-0.3in}
%     \caption{Slack tracking and drop decision hardware.}
%     \label{fig:policies.trade_off}
%     \vspace{-0.2in}
%   \end{center}
% \end{figure}
% 
% Another possible method is to make the dropping decisions somewhere in between
% source-only dropping and unrestricted dropping. From the graph in 
% Figure~\ref{fig:policies.dataflow_graph}, we can see that if the dropping
% decision is made at event {\tt C} then we can skip event {\tt E} with no wasted
% work. If we instead choose to perform monitoring for event {\tt C}, then we want to perform all
% monitoring on that flow. Similarly, event {\tt F} creates a decision point for
% the bottom flow that will result in no wasted work and dropping event {\tt A}
% allows the entire shown metadata flow to be dropped with no wasted work. If the
% program can be
% analyzed or profiled to identify these instructions which, if dropped, lead to
% no wasted work, then this information can be used at run-time to minimize the
% amount of wasted work. We refer to this policy as \emph{sub-flow dropping}.
% Figure~\ref{fig:policies.min_drop} shows the points were dropping decisions are
% made for this policy.
% Sub-flow dropping is a coarser-grained decision than unrestricted dropping, but
% finer-grained that source-only dropping. Thus, its ability to match overheads is
% expected to sit between these other two policies. Similarly, there still exists
% edge cases where wasted work can occur, but typically we expect much less
% wasted work than unrestricted 
% dropping. Thus, we expect the coverage achieved by sub-flow dropping for a
% certain overhead to fall between source-only and unrestricted dropping. These three
% dropping policies create a trade-off space between coverage achieved and
% ability to match an overhead target.
% Figure~\ref{fig:policies.trade_off} summarizes this trade-off between coverage
% and ability to match overhead.

### 2014-05-30 related.tex
Remove sub-flow policy.

% Limited Monitoring
In terms of partial monitoring, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. These projects are targeting a similar problem
to the one we address in this paper. However, both projects are focused on
software-based monitoring and thus their mechanisms modify the software
monitoring framework in order to enable or disable monitoring. Instead, our
architecture provides a general hardware mechanism to control overheads of
parallel monitoring architectures. In addition, these works prevented
false positives by enabling and disabling monitoring using only a source-dropping
policy. Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring in hard real-time systems. Their architecture performs unrestricted 
dropping in order to guarantee strict deadlines. Our system allows for a
trade-off between choosing source-only dropping, unrestricted dropping, or sub-flow 
dropping depending on the needs of the designer or user which has not been
explored by these previous works.

>>>>

% Limited Monitoring
In terms of partial monitoring, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. These projects are targeting a similar problem
to the one we address in this paper. However, both projects are focused on
software-based monitoring and thus their mechanisms modify the software
monitoring framework in order to enable or disable monitoring. Instead, our
architecture provides a general hardware mechanism to control overheads of
parallel monitoring architectures. In addition, these works prevented
false positives by enabling and disabling monitoring using only a source-dropping
policy. Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring in hard real-time systems. Their architecture performs unrestricted 
dropping in order to guarantee strict deadlines. 
Our system allows either source-only dropping or unrestricted dropping to be performed.
This allows the designer or user to choose the appropriate policy depending on
the monitoring scheme which has not been previously explored.
